Unsupervised embedding of trajectories captures the latent structure of mobility

### 2021-02-18 paper/current/main.tex
distance typo

We compare the performance of the embedding distance to many baselines.
These include distances derived from simpler embedding approaches, such as Singular Value Decomposition (SVD) and a Laplacian Eigenmap embedding performed on the underlying co-occurrence matrix.
We also use network-based distances, calculating vectors using a Personalized Page Rank approach and measuring the distance between them using cosine distance and Jensen-Shannon Divergence (see \SI).
Finally, we compare the embedding distnace against embeddings calculated through direct matrix factorization, following the approach that \textit{word2vec} implicitley approximates~\autocite{levy2014neural}.

>>>>

We compare the performance of the embedding distance to many baselines.
These include distances derived from simpler embedding approaches, such as Singular Value Decomposition (SVD) and a Laplacian Eigenmap embedding performed on the underlying co-occurrence matrix.
We also use network-based distances, calculating vectors using a Personalized Page Rank approach and measuring the distance between them using cosine distance and Jensen-Shannon Divergence (see \SI).
Finally, we compare the embedding distance against embeddings calculated through direct matrix factorization, following the approach that \textit{word2vec} implicitley approximates~\autocite{levy2014neural}.
